\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------%
\begin{center}
\vspace{-20pt}
    \textbf{\Large \scshape Prabhav Karve} \\ \vspace{1pt}
    
    \small {San Jose, CA, US} $|$ (585) 957 3674 $|$ \href{mailto:pk6004@g.rit.edu}{{\underline{pk6004@rit.edu}}} $|$ 
    \href{https://www.linkedin.com/in/prabhav-karve-11300a145/}{{\underline{LinkedIn}}} $|$
    \href{https://prabhav-karve-portfolio2-0.vercel.app/}{{\underline{Portfolio}}} $|$
    {Open to relocation }
\vspace{-3pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Rochester Institute of Technology}{Aug 2023 - Dec 2025}
      {Master of Science in Computer Science (3.8/4.0)}{Rochester, NY, USA}
      {}
      \vspace{-5pt}
      \resumeSubheading
       {International Institute of Information Technology }{Aug 2017 - Jul 2021}
      {Bachelor of Engineering in Information Technology (3.5/4.0)}{Pune, MH, India}
      {}
      \vspace{-6pt}
  \resumeSubHeadingListEnd



%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
   \small{\item{
     \textbf{Languages}{: Java, Python, JavaScript, TypeScript, C++, GoLang, GraphQL} \\
     \textbf{Tools}{: PowerBI, PySpark, Kafka, Airflow, Azure Data factory, Jenkin, Git, BitBucket, LLM} \\
     \textbf{Databases}{: MS SQL, PostgreSQL, Snowflake, Teradata, Oracle PL/SQL, MongoDB}\\
     \textbf{Frameworks}{: React.js, Node.js, Spring Boot, FastAPI, LangChain, RAG, Agile } \\
     \textbf{Cloud}{: Azure Functions, Blob Storage, AWS EC2, RDS, S3, Lambda, Terraform} \\
     \textbf{AI Tools}{: Copilot, Cursor, Claude Code, Gemini } 
    }}
    
 \end{itemize}



%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \vspace{1pt}
    \resumeSubheading
      {Rochester Regional Health}{Jun 2025 - Dec 2025}
      {Software Engineer Intern}{Rochester, NY}
    \resumeItemListStart
       \vspace{-6pt}
            \resumeItem{Delivered healthcare analytics reports by integrating data from 23+ sources through ETL pipelines built in Azure Data Factory to predict expense, revenue and healthcare trend using machine learning.}
            \resumeItem
            {Automated data collection and data load into 27+ KPI tables in Snowflake  by developing Python scripts to extract data from REST APIs, improving data availability and reporting speed.}
            \resumeItem{Rectified financial report accuracy to 100\% by optimizing 40+ scripts using pandas and Cortex Generative AI in snowflake's LLM tools.}
            \resumeItem{Designed 17+ interactive Power BI dashboards to visualize work-time and expense KPI for heath-care.}
            \vspace{3pt}
    \resumeItemListEnd

    \resumeSubheading
      {Accenture}{Sept 2021 - Mar 2023}
      {Associate Software Engineer}{Pune, India}
     
      \resumeItemListStart
       \vspace{-6pt}
            \resumeItem{Developed a Business Intelligence platform for Ireland’s biggest financial service using Java and Snowflake.}
            \resumeItem{Implemented 20+ Spring Boot RESTful APIs and deployed it on Jenkins CI/CD Pipeline.}
            \resumeItem{Enabled data availability at latency less than 100 ms by ingesting near-real-time transactional data using Kafka .}
            \resumeItem{ Constructed over 50 SQL scripts and and orchestrated scalable ETL pipelines on Airflow for regulatory financial reporting.}
            \resumeItem{Collaborated across the data modeling team to build the target schemas on Snowflake preliminary to the data visualization on Power BI.}
            \resumeItem{Resolved 77 \% of the total resolved defects in FY 2022 - 23 by designing defect resolutions.}
            \resumeItem{Enhanced the deployment efficiency by automating 10+ monotonous validation checks using Python.}
      \resumeItemListEnd

      \resumeSubheading
      {PS - IT Solutions}{Aug 2019 - Aug 2020}
      {Software Engineer Intern}{Pune, India}
     
      \resumeItemListStart
       \vspace{-6pt}
            \resumeItem{Launched an invoice management application in React.js and Java backend for a logistics warehouse serving 750 agents.}
            \resumeItem{ Created user interface and hosted the Java Spring boot APIs on AWS EC2. Integrated the MySQL database on RDS.}
            \resumeItem{Reduced the invoice validation time to minutes, achieving 15\% more efficient logs FY in 2019–2020.}
            \resumeItem{Achieved significant decreased paper invoices by 75\% through digital transformation.}
      \resumeItemListEnd
\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

    \resumeProjectHeading
          {\textbf{RAG system for financial statement intelligence }$|$ {(Next.js, Python, PostgreSQL, FAISS, LangChain, GraphQL)}}{}
          \resumeItemListStart
          \vspace{4pt}
            \resumeItem{Devised a RAG platform to semantically analyze 30+ financial statements and answer complex, stock-related queries.}
            \resumeItem{Implemented MCP pipeline leveraging FAISS for vector storage and LangChain for 95\% accurate context-driven retrieval of insights.}
            \resumeItem{Created a GraphQL-based API layer on PostgreSQL and built a Next.js frontend for an intuitive, question-answer interface.}
            \resumeItem{Containerized using Docker and deployed on AWS EC2 with RDS for PostgreSQL for scalable cloud hosting.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Students Accommodation rental }$|$ {(React.js, Python, FastAPI, DynamoDB, Docker, Jenkins)}}{}
          \resumeItemListStart
          \vspace{4pt}
            \resumeItem{Led a team of three to launch a platform for international students to search or sublet residences in 50+ cities.}
            \resumeItem{Loaded with features like Authentication, Search Filters, Messaging, allowing seamless user experience.}
            \resumeItem{Composed a responsive UI with React.js and used FastAPI to handle 14 endpoints for secure server communication.}
            \resumeItem{Engineered a Jenkins build pipeline (CI/CD) with containerization using Docker for quick deployment and release.}
            \vspace{-6pt}

          \resumeItemListEnd
    \resumeSubHeadingListEnd


\section{Achievements and Awards}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{{Received 40\% performance-based scholarship at Rochester Institute of Technology: 27000\$.} \\{Authored and published a research paper in Springer’s conference on “Conversational image captioning in YOLO and LSTM”.} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}