\documentclass[letterpaper,10.5pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}


\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{center}
\vspace{-20pt}
    \textbf{\Large \scshape Dharmik Patel} \\ \vspace{1pt}
    \small +1-(585)-224-5490 $|$ \href{mailto:dp9208@g.rit.edu}{{\underline{dharmik7601@gmail.com}}} $|$
    \href{http://linkedin.com/in/dharmik7601}{\underline{linkedin.com/in/dharmik7601}} $|$
    \href{http://github.com/Dharmik7601}{\underline{github.com/Dharmik7601}} $|$
    {Rochester, NY, USA}
\vspace{-10pt}
\end{center}
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
      \resumeSubheading{Amazon Web Services (AWS) \textbar{} \footnotesize{Bedrock, Lambda, CDK, Java, TypeScript}}{May 2025 - Aug 2025}
      {Software Development Engineer Intern}{East Palo Alto, CA, USA}
       \resumeItemListStart
       \vspace{-6pt}
            \resumeItem{Engineered an internal LLM analyzer tool using AWS Bedrock for code reviews across 4 key areas (security, performance, style, test coverage), working within an agile framework.}
            \resumeItem{Authored design document and deployment of a secure, serverless application using the AWS CDK (IaC), orchestrating 8+ core AWS services including Lambda, Bedrock, Step Functions, Opensearch, and DynamoDB.}
            \resumeItem{Built a data ingestion pipeline to fetch and update over 5,000+ high-value internal data sources, enhancing the LLM's contextual awareness for impact analysis.}
            \resumeItem{Secured the application's VPC and all services using precise IAM roles and granular Security Group (ingress/egress) rules to enforce least-privilege access.}
    \resumeItemListEnd
    \resumeSubheading
      {Acute Informatics Pvt. Ltd. \textbar{} \footnotesize{MERN, REST APIs, JWT, AWS, MongoDB}}{Dec 2022 -- Apr 2023 }
      {Software Developer Intern}{Ahmedabad, GJ, India}
       \resumeItemListStart
       \vspace{-6pt}
            \resumeItem{Orchestrated a 5-service microservice application application using Docker and Kubernetes, authoring 10+ configuration files to automate scaling and updates, which reduced new environment setup time for the team by over 50\%.}
            \resumeItem{Established an event-driven architecture using RabbitMQ to decouple a central API Gateway from backend services, successfully processing and delivering over 1,000+ automated email notifications daily.}
            \resumeItem{Developed and containerized microservices, including a Flask authentication service using MySQL and a video processing worker that leveraged MongoDB GridFS for storing large media files.}
    \resumeItemListEnd
    \resumeSubheading
      {WPServiceDesk Pvt. Ltd. \textbar{} \footnotesize{Flask, Kubernetes, Docker, RabbitMQ, CI/CD}}{May 2022 -- Sep 2022}
      {Software Developer Intern}{Ahmedabad, GJ, India}
      \resumeItemListStart
       \vspace{-6pt}
            \resumeItem{Built 2 full-stack MERN applications (Loan Origination \& Billing System) from scratch, delivering 15+ features including KYC document uploads, invoice generation, and admin/user panels.}
            \resumeItem{Implemented and secured 40+ REST API endpoints for both applications using Node.js, Express, and JWT for authentication with bcrypt hashing.}
            \resumeItem{Designed and managed 12+ MongoDB data models and integrated key AWS services for features like file storage (S3) and automated notifications (SES).}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Distributed File System \textbar{} \footnotesize{C++, P2P, AES Encryption, CAS} }}{}
          \resumeItemListStart
            \resumeItem{Created a peer-to-peer distributed file system in C++, facilitating decentralized file storage and data retrieval across 10+ nodes.}
            \resumeItem{Devised secure file storage and retrieval mechanisms, incorporating encryption (AES) and hashing (SHA-256, MD5) for data integrity and security.}
            \resumeItem{Incorporated homomorphic content-addressable storage (CAS) across 10 nodes, achieving a 15\% reduction in data redundancy and improving data retrieval speeds.}
            \resumeItem{Constructed a storage engine capable of efficient file operations, including secure storing, retrieval, deletion, and verification across a divided network.}
          \resumeItemListEnd

        \resumeProjectHeading
          {\textbf{Go HTTP Server \textbar{} \footnotesize{Go, TCP, Concurrency, HTTP/1.1 Parser}}}{}
          \resumeItemListStart
            \resumeItem{Developed a custom HTTP server from scratch in Go, utilizing low-level TCP sockets to manage and process raw HTTP requests reducing the final binary size by an estimated 50\% by avoiding external runtime dependencies.}
            \resumeItem{Devised a resilient request parser using a finite state machine to handle the sequential states of an HTTP request ensuring compliance with HTTP/1.1 protocol standards.}
            \resumeItem{Leveraged Go's native concurrency model that allows the server to handle over 1,000+ connections, ensuring high availability and responsiveness under load.}
            \resumeItem{Implemented multi-type content serving (video files, proxied requests) and chunked transfer encoding with SHA-256 checksums for data integrity.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
%-------------------------------------------
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C++, Go (GoLang), Java, TypeScript, JavaScript} \\
     \textbf{DevOps, Cloud, \& Tools}{: Docker, Kubernetes, RabbitMQ, AWS, GCP, Azure, Terraform, CDK, Git, Postman} \\
     \textbf{Databases \& Data Stores}{: MySQL, MongoDB, PostgreSQL, DynamoDB, Opensearch, S3} \\
     \textbf{Backend Frameworks}{: Flask, Spring Boot, FastAPI, Django, Node.js, Express.js, Gin }
    }}
 \end{itemize}
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Rochester Institute of Technology}{Aug 2023 -- Dec 2025}
      {MS in Computer Science \textbar{} \textbf{Advanced Algorithms, Artificial Intelligence, Big Data Analytics}}{Rochester, NY, USA}
      \vspace{-5pt}
    \resumeSubheading
      {Indus University}{Aug 2019 -- Jun 2023}
      {BE in Computer Science \textbar{} \textbf{Software Engineering, Cloud Computing, Distributed Systems}}{Ahmedabad, GJ, India}
      \vspace{-5pt}
  \resumeSubHeadingListEnd
\end{document}
